### 2021-10-20 text/outline/outline.tex
add critical value proof

\subsubsection{Critical values of }

% \subsubsection{Bayes-optimal decision boundary as a critical value}
% Let $c_\textrm{bayes} = \beta^g_0 + (1/2)\beta^g_1.$ We show that $c = c_\textrm{bayes}$ is a critical value of $\gamma$ for $\pi = 1/2$ and fixed $(\beta^g_0, \beta^g_1)$ , i.e, $$\frac{\partial  \gamma(\beta^g_0, \beta^g_1, c, 1/2)}{ \partial c} \vline_{[c = c_\textrm{bayes}]} = 0.$$ By quotient rule,
% $$ \frac{\partial  \gamma(\beta^g_0, \beta^g_1, c, 1/2)}{ \partial c} = \frac{g'(\cdot, c) h(\cdot, c) - g(\cdot, c) h'(\cdot, c)}{\left[ h(\cdot, c) \right]^2}.$$ First,
% $$g'(\cdot, c) = - f( \beta^g_0 + \beta^g_1 - c ) + f(\beta^g_0 - c).$$ Second, 
% \begin{multline*}
% h'(\cdot, c) = -[f(\beta^g_0 - c)  + f( \beta^g_0 + \beta^g_1 - c )]  \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right] \\ +[ f(c - \beta^g_0) + f(c - \beta^g_0 - \beta^g_1) ] \left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right].
% \end{multline*}
% Evaluating $g'(\cdot, c)$ and $h'(\cdot, c)$ at $c = c_\textrm{bayes} $, we find that
% $$g'(\beta^g_0 + (1/2) \beta^g_1) = -f(\beta^g_1/2) + f(- \beta^g_1/2) = -f(\beta^g_1/2) + f(\beta^g_1/2) = 0,$$ where the second equality follows from the evenness of $f$. Similarly, 
% \begin{multline*}
% h'(\beta^g_0 + (1/2) \beta^g_1) = - \left[ f( -\beta^g_1/2) + f( \beta^g_1/2 ) \right] \left[ \int_{-\infty}^{ \beta^g_1/2} f + \int_{-\infty}^{ -\beta^g_1/2} f \right] + \\ \left[ f( \beta^g_1/2) + f( -\beta^g_1/2 ) \right] \left[ \int_{-\infty}^{ -\beta^g_1/2} f + \int_{-\infty}^{ \beta^g_1/2 f} \right] = 0.
% \end{multline*}
% We conclude that
% $$ \frac{\partial \gamma(\beta^g_0, \beta^g_1, c, 1/2)}{ \partial c} \vline_{[c = c_\textrm{bayes}]} = \frac{0\cdot h(\cdot, c_\textrm{bayes}) - g(\cdot, c_\textrm{bayes}) \cdot 0}{ h(\cdot, c_\textrm{bayes})^2} = 0.$$ Finally, because asymptotic bias $b$ can be expressed in terms of $\gamma$ as $$b(\beta^g_0. \beta^g_1, c, \pi) = \beta^m_1 \left[ 1 - \gamma(\beta^g_0, \beta^g_1, c, \pi) \right],$$ it follows that $c = c_\textrm{bayes}$ is a critical value of $b$ for $\pi = 1/2$ and fixed $(\beta^g_0, \beta^g_1)$.

>>>>

\subsubsection{Bayes-optimal decision boundary as a critical value of $\gamma$}
Let $c_\textrm{bayes} = \beta^g_0 + (1/2)\beta^g_1.$ We show that $c = c_\textrm{bayes}$ is a critical value of $\gamma$ for $\pi = 1/2$ and given $\beta^g_1$, i.e, $$D_2 \gamma (\beta^g_1, c_\textrm{bayes}, 1/2) = 0.$$ By the quotient rule,
\begin{multline}\label{quotient_rule}
D_2\gamma(\beta^g_1, c, 1/2) \\ = \frac{(1/2) D_2g(\beta^g_1, c, 1/2) h(\beta^g_1, c, 1/2) - (1/2) g(\beta^g_1, c, 1/2) D_2 h(\beta^g_1, c, 1/2)}{[h(\beta^g_1, c, \pi)]^2} \\ = \frac{\left[4(1/2) D_2g(\beta^g_1, c, 1/2)\right] h(\beta^g_1, c, 1/2) - (1/2) g(\beta^g_1, c, 1/2) \left[4 D_2 h(\beta^g_1, c, 1/2)\right]}{[2h(\beta^g_1, c, \pi)]^2},
\end{multline}
where the second equality multiplies both numerator and denominator by $4$. We have by (\ref{dg_dc}) that
\begin{multline}\label{dg_dc_bayes}
4 \cdot (1/2) \cdot D_2 g(\beta^g_1, c_\textrm{bayes}, 1/2)  = f( \beta^g_1/2) - f( -\beta^g_1/2) \\ = f(\beta^g_1/2) - f(\beta^g_1/2) = 0.
\end{multline}
Next, we have by (\ref{dh_dc}) that
\begin{multline}\label{dh_dc_bayes}
4 \cdot D_2 h(\beta^g_1, c_\textrm{bayes}, \pi) = [f( \beta^g_1/2) + f( -\beta^g_1/2)] \cdot \\ \left[  \int_{-\infty}^{-\beta^g_1/2} f + \int_{-\infty}^{\beta^g_1/2} f - \int_{-\infty}^{\beta^g_1/2} f - \int_{-\infty}^{-\beta^g_1/2} f \right] = 0.
\end{multline}
Plugging in (\ref{dh_dc_bayes}) and (\ref{dg_dc_bayes}) to (\ref{quotient_rule}), we find that 
$$D_2(\beta^g_1, c_\textrm{bayes}, 1/2) = 0.$$

% $$g'(\cdot, c) = - f( \beta^g_0 + \beta^g_1 - c ) + f(\beta^g_0 - c).$$ Second, 
% \begin{multline*}
% h'(\cdot, c) = -[f(\beta^g_0 - c)  + f( \beta^g_0 + \beta^g_1 - c )]  \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right] \\ +[ f(c - \beta^g_0) + f(c - \beta^g_0 - \beta^g_1) ] \left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right].
% \end{multline*}
% Evaluating $g'(\cdot, c)$ and $h'(\cdot, c)$ at $c = c_\textrm{bayes} $, we find that
% $$g'(\beta^g_0 + (1/2) \beta^g_1) = -f(\beta^g_1/2) + f(- \beta^g_1/2) = -f(\beta^g_1/2) + f(\beta^g_1/2) = 0,$$ where the second equality follows from the evenness of $f$. Similarly, 
% \begin{multline*}
% h'(\beta^g_0 + (1/2) \beta^g_1) = - \left[ f( -\beta^g_1/2) + f( \beta^g_1/2 ) \right] \left[ \int_{-\infty}^{ \beta^g_1/2} f + \int_{-\infty}^{ -\beta^g_1/2} f \right] + \\ \left[ f( \beta^g_1/2) + f( -\beta^g_1/2 ) \right] \left[ \int_{-\infty}^{ -\beta^g_1/2} f + \int_{-\infty}^{ \beta^g_1/2 f} \right] = 0.
% \end{multline*}
% We conclude that
% $$ \frac{\partial \gamma(\beta^g_0, \beta^g_1, c, 1/2)}{ \partial c} \vline_{[c = c_\textrm{bayes}]} = \frac{0\cdot h(\cdot, c_\textrm{bayes}) - g(\cdot, c_\textrm{bayes}) \cdot 0}{ h(\cdot, c_\textrm{bayes})^2} = 0.$$ Finally, because asymptotic bias $b$ can be expressed in terms of $\gamma$ as $$b(\beta^g_0. \beta^g_1, c, \pi) = \beta^m_1 \left[ 1 - \gamma(\beta^g_0, \beta^g_1, c, \pi) \right],$$ it follows that $c = c_\textrm{bayes}$ is a critical value of $b$ for $\pi = 1/2$ and fixed $(\beta^g_0, \beta^g_1)$.
